---
title: "BOAST Utilities"
author: EducationShinyAppTeam
date: November 13, 2019
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

Used to provide reusable [components](https://shiny.rstudio.com/articles/html-tags.html), [gadgets](https://shiny.rstudio.com/articles/gadgets.html), and [modules](https://shiny.rstudio.com/articles/modules.html) for the [BOAST](https://github.com/EducationShinyAppTeam/BOAST) project.

## Installation

You can install this version of boastUtils from [GitHub](https://github.com/) with:

```{r}
devtools::install_github("EducationShinyAppTeam/boastUtils")
```

**Troubleshooting:**
- [Error: (converted from warning) package 'xyz' was built under R version x.y.z](https://github.com/r-lib/remotes/issues/403#issuecomment-513891775)

Create an [issue](https://github.com/EducationShinyAppTeam/boastUtils/issues) if the problem is not solved by one of the above.

## Creating an App

One way to accomplish serving a more standardized codebase was to provide a wrapper for the default [shinyApp](https://shiny.rstudio.com/reference/shiny/latest/shinyApp.html) function. Instead of including the `shiny` package, include `boastUtils` and write your app as normal. Be sure to replace `shinyApp` with `boastApp`.

##### Example app.R
```{r}
library(boastUtils)

ui <- fluidPage(
  # ... ui definitions ...
)

server <- function(input, output, session){
  # ... server logic ...
}

boastApp(ui = ui, server = server)
```


## Configuration

We currently have one config option available which disables xAPI logging.

##### Example app.R
```{r}
boastApp(ui = ui, server = server, config = list("log" = FALSE))
```